Wildcard: Spreadsheet-Driven Customization of Web Applications

### 2020-01-13 paper.tex
finished

This paper is best viewed in the online version, which includes videos demonstrating the interface: \url{https://www.geoffreylitt.com/wildcard/}
\end{abstract}

@@

Here are some examples of using Wildcard to customize websites in useful
ways.{ These demos are best viewed as videos in the online version of
this paper (\url{https://www.geoffreylitt.com/wildcard}).}

@@

Another aspect of providing a low floor is providing an ``in-place
toolchain'' \autocite{inkandswitch2019}: minimizing the effort of moving
from using to customizing, by making customization tools available in
the same environment where the user is already using the software. This
quality is distinct from the level of technical skill needed to use the
tool. For example, setting up a workflow trigger in an end user
programming system like \href{https://ifttt.com/}{IFTTT} does not
require much technical skill, but does require leaving the user's normal
software and entering a separate environment; conversely, running a
Javascript snippet in the browser console requires programming skills,
but can be done immediately and casually in the flow of using a website.

>>>>

This paper is best viewed in the online version, which includes videos demonstrating the interface: \url{https://www.geoffreylitt.com/wildcard/salon2020}
\end{abstract}

@@

Here are some examples of using Wildcard to customize websites in useful
ways.{ These demos are best viewed as videos in the online version of
this paper (\url{https://www.geoffreylitt.com/wildcard/salon2020}).}

@@

Another aspect of providing a low floor is providing an ``in-place
toolchain'' \autocite{2019}: minimizing the effort of moving from using
to customizing, by making customization tools available in the same
environment where the user is already using the software. This quality
is distinct from the level of technical skill needed to use the tool.
For example, setting up a workflow trigger in an end user programming
system like \href{https://ifttt.com/}{IFTTT} does not require much
technical skill, but does require leaving the user's normal software and
entering a separate environment; conversely, running a Javascript
snippet in the browser console requires programming skills, but can be
done immediately and casually in the flow of using a website.
